The Effects of weather on maize yield: New evidence from Kenya

### 2018-12-26 writing/draft3/draft19.tex
writ

We will now discuss and compare the results of the models for the subsamples of the ASAL counties (the third and fourth columns of table~\ref{MainEst}) and the non-ASAL counties (the fifth and sixth columns of table~\ref{MainEst}). Interestingly, different predictors were  found significant for the two subsamples. Regarding the subsample of the ASAL counties, the only significant fixed effects are average seasonal temperature and length and number of dry spells. All three variables have a negative sign. On the other hand, the variables which were found significant for the subsample of the non-ASAL counties include seasonal precipitation and its square with a positive and a negative sign, respectively and CV of temperature which has a positive sign as in the case of the entire sample. According to the F-statistic, the most important explanatory variables for the ASAL counties are number of dry spells with F-statistic equal to $8.032$ and length of the longest dry spell with F-value equal to $6.841$. The F-statistic of the average temperature is $5.409$ and it lower than zero for the remaining predictors. However, according to the magnitude of the standardised coefficient, the average temperature would be the most important as the coefficient is equal to $-0.214$ while it is equal to $-0.156$ and $-0.181$ for the number of dry spells and the length of maximum dry spell, respectively. With regard to the subsample of the non-ASAL counties, the most important explanatory variables based on the F-statistic are precipitation and its square. The F-statistic of the squared values of precipitation is $23.384$ and its value for the linear term of precipitation is $19.140$, while the variable with the third highest F-statistic is CV of temperature with the F-statistic equal to $5.372$, hence, the difference in importance of the precipitation and CV of temperature is relatively large. The standardised coefficient of squared precipitation is equal to $-0.127$, the coefficient of the linear term of precipitation is $0.244$ and the standardised coefficient of CV of temperature is $0.058$. In terms of the magnitude of the coefficients, the average temperature is also relatively important as the value of the coefficient is $-0.128$. However, average temperature is insignificant according to the Satterthwaite's p-value and its F-statistic is also relatively small, in particular $1.528$.

>>>>

We will now discuss and compare the results of the models based on the subsample of the ASAL counties (the third and fourth columns of table~\ref{MainEst}) and the model based on the subsample of the non-ASAL counties (the fifth and sixth columns of table~\ref{MainEst}). Interestingly, different predictors were found significant for each of the two subsamples. Regarding the subsample of the ASAL counties, the only significant fixed effects are average seasonal temperature and length and number of dry spells. According to our expectation, all three variables have a negative sign. On the other hand, the variables which were found significant for the subsample of the non-ASAL counties include seasonal precipitation (positive) and its square (negative) and CV of temperature (positive). According to the F-statistics, the most important explanatory variables for the ASAL counties are number of dry spells and length of the longest dry spell with values of the F-statistics equal to $8.032$ and $6.841$, respectively. The F-statistic of the average temperature is $5.409$ and the F-statistics of the remaining predictors are lower than zero. However, according to the magnitude of the standardised coefficients, the average temperature would be the most important as the coefficient is equal to $-0.214$ while it is equal to $-0.156$ and $-0.181$ for the number of dry spells and the length of maximum dry spell, respectively. With regard to the subsample of the non-ASAL counties, the most important explanatory variables based on the F-statistic are precipitation and its square. The F-statistic of the squared values of precipitation is $23.384$ and its value for the linear term of precipitation is $19.140$, while the variable with the third highest F-statistic is CV of temperature with the F-statistic equal to $5.372$, hence, the difference in importance of the precipitation and CV of temperature is relatively large. The standardised coefficient of squared precipitation is equal to $-0.127$, the coefficient of the linear term of precipitation is $0.244$ and the standardised coefficient of CV of temperature is $0.058$. In terms of the magnitude of the coefficients, the average temperature is also relatively important as the value of the coefficient is $-0.128$. However, average temperature is insignificant according to the Satterthwaite's p-value and its F-statistic is also relatively small, in particular $1.528$.
